### 2018-11-29 2018_nips_vigil_poster/main.tex
Add better QR codes & finalize poster.

\headerbox{Links}{name=links,column=0,below=s-mac}{
	\vspace{-15pt}
	\begin{minipage}[H]{0.4\textwidth}
		\begin{figure}[H]
			\includegraphics[width=0.4\textwidth]{../img/doc_qr_code.png}
			\vspace{-10pt}
			\caption{Documentation.}
			\label{fig:qr_doc}
		\end{figure}
	\end{minipage}
	\hfill
	\begin{minipage}[H]{0.4\textwidth}
		\begin{figure}[H]
			\includegraphics[width=0.4\textwidth]{../img/github_repo_qr_code.png}
			\vspace{-10pt}
			\caption{GitHub repo.}
			\label{fig:qr_github}
		\end{figure}
	\end{minipage}
}

\headerbox{The CLEVR \& CoGenT datasets}{name=datasets, column=1}{
	\vspace{-10pt}
	\begin{figure}[H]
		\includegraphics[width=0.4\textwidth]{../img/teaser.jpg}
		\caption{\textit{How many objects are either small cylinders or red things?}}
		\label{fig:clevr_task}
	\end{figure}
	\vspace{-10pt}
	\begin{itemize}
	  	\compresslist
	  	\item[$\bullet$] The authors~\cite{johnson2017clevr} also introduced CLEVR-CoGenT, to evaluate how well a model can learn relations and compositional concepts.
	  	\item[$\bullet$] Similar to CLEVR, but with two conditions, as follows:
	\end{itemize}
	\vspace{-10pt}
	\begin{table}[H]
		\centering
		\begin{tabular}{llll}
			\toprule
			Dataset        & Cubes              & Cylinders &  Spheres         \\
			\midrule
			CLEVR   &  any color &  any color        &    any color    \\
			CLEVR CoGenT-A & gray / blue / brown / yellow  & red / green / purple / cyan       &    any color  \\
			CLEVR CoGenT-B  & red / green / purple / cyan &   gray / blue / brown / yellow       &      any color  \\
			\bottomrule
		\end{tabular}
		\caption{Colors/shapes combinations present in CLEVR, CoGenT-A and CoGenT-B datasets.}
		\label{tab:cogent_conditions}
	\end{table}

@@

\headerbox{Experiments \& Results}{name=experiments, column=1, below=datasets}{

CLEVR \& CoGenT accuracies for the MAC \& S-MAC models:
	\begin{table}[H]
	\centering
	\scalebox{1}{
	\begin{tabular}{cccccccc}
		\toprule
		\multirow{2}{*}{Model} & \multicolumn{3}{c}{Training} &  \multicolumn{2}{c}{Fine-tuning} & \multicolumn{2}{c}{Test} \\
		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
		& Dataset                & Time [h:m] & Acc [\%]          & Dataset & Acc [\%]  & Dataset & Acc [\%] \\
		\midrule
		MAC & CLEVR  & 30:52  & 96.70 & --   & --  & CLEVR    & 96.17 \\
		\cmidrule{1-8}
		\cmidrule{1-8}

@@

		\bottomrule

	\end{tabular}}
	\label{tab:data_properties}
\end{table}

\begin{description}
	\item[$\bullet$] Our experiments on zero-short learning show that the MAC model has poor performance in line with
	the other models in the literature.
	\item[$\bullet$] With fine-tuning, the MAC model matches state of
	the art accuracy
	\item[$\bullet$]Remains an interesting problem to investigate how we can train it to disentangle the concepts of shape and color.
	\item[$\bullet$] Experiments can be reproduced by following the \textbf{mi-prometheus}  documentation
\end{description}

@@

\headerbox{MAC drawbacks on CLEVR}{name=baseline, column=1, below=experiments}{

	\begin{figure}[H]
	\centering
				\includegraphics[width=0.60\textwidth]{../img/fail_mac_cogent_b_shape.png}

\end{figure}

\begin{description}
	\item[$\bullet$] The question reads as: \textit{There is a large gray thing that is on the right side of the big gray cylinder left of the large ball that is on the right side if the cyan rubber sphere; what is its shape? Predicted answer: Cylinder - Truth: Cube}

\end{description}

\headerbox{References}{name=references, column=1, below=baseline}{
	\small
	\vspace{-8pt}
	\renewcommand{\refname}{}
	\bibliographystyle{alpha}
	\bibliography{../vigil_bibliography}
	\normalsize
	\textsl{}
}

\end{poster}

\end{document}

>>>>

\headerbox{Links}{name=links,column=0,below=s-mac}{
	\vspace{-15pt}
	\begin{minipage}[H]{0.4\textwidth}
		\begin{figure}[H]
			\includegraphics[width=0.4\textwidth]{../img/arxiv_paper_qr_code.png}
			\vspace{-10pt}
			\caption{Paper on arXiv.}
			\label{fig:qr_arxiv}
		\end{figure}
	\end{minipage}
	\hfill
	\begin{minipage}[H]{0.4\textwidth}
		\begin{figure}[H]
			\includegraphics[width=0.4\textwidth]{../img/reproducible_research_qr_code.png}
			\vspace{-10pt}
			\caption{\textbf{How to reproduce the experiments.}}
			\label{fig:qr_repro_research}
		\end{figure}
	\end{minipage}
}

\headerbox{The CLEVR \& CoGenT datasets}{name=datasets, column=1}{
	\vspace{-10pt}
	\begin{figure}[H]
		\includegraphics[width=0.4\textwidth]{../img/teaser.jpg}
		\caption{\textit{How many objects are either small cylinders or red things?}}
		\label{fig:clevr_task}
	\end{figure}
	\vspace{-20pt}
	\begin{itemize}
	  	\compresslist
	  	\item[$\bullet$] The authors~\cite{johnson2017clevr} also introduced CLEVR-CoGenT, to evaluate how well a model can learn relations and compositional concepts.
	  	\item[$\bullet$] Similar to CLEVR, but with two conditions, as follows:
	\end{itemize}
	\vspace{-10pt}
	\begin{table}[H]
		\centering
		\begin{tabular}{llll}
			\toprule
			Dataset        & Cubes              & Cylinders &  Spheres         \\
			\midrule
			CLEVR   &  any color &  any color        &    any color    \\
			CLEVR CoGenT-A & gray / blue / brown / yellow  & red / green / purple / cyan       &    any color  \\
			CLEVR CoGenT-B  & red / green / purple / cyan &   gray / blue / brown / yellow       &      any color  \\
			\bottomrule
		\end{tabular}
		\caption{Colors/shapes combinations present in CLEVR, CoGenT-A and CoGenT-B datasets.}
		\label{tab:cogent_conditions}
	\end{table}

@@

\headerbox{Experiments \& Results}{name=experiments, column=1, below=datasets}{
	\vspace{-10pt}
	\begin{table}[H]
	\centering
	\scalebox{1}{
	\begin{tabular}{cccccccc}
		\toprule
		\multirow{2}{*}{Model} & \multicolumn{3}{c}{Training} &  \multicolumn{2}{c}{Fine-tuning} & \multicolumn{2}{c}{Test} \\
		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
		& Dataset                & Time [h:m] & Acc [\%]          & Dataset & Acc [\%]  & Dataset & Acc [\%] \\
		\midrule
		MAC & CLEVR  & 30:52  & 96.70 & --   & --  & CLEVR    & 96.17 \\
		\cmidrule{1-8}
		\cmidrule{1-8}

@@

		\bottomrule
	\end{tabular}}
	\caption{CLEVR \& CoGenT accuracies for the MAC \& S-MAC models.}
	\label{tab:data_properties}
\end{table}
\vspace{-20pt}

\begin{itemize}
	\compresslist
	\item[$\bullet$] Our experiments on \emph{zero-shot learning} show that both models have poor performance, in line with
	the other models in the literature.
	\item[$\bullet$] With fine-tuning, both MAC models match state-of-the-art accuracy (a 15pts increase).
	\item[$\bullet$] \textbf{S-MAC presents a 10\% speed-up in training time and comparable accuracy.}
	\item[$\bullet$] Finetuning CLEVR-trained models on CoGenT-A or -B hurts their generalization capabilities.
	\item[$\rightarrow$] \emph{Zero-shot learning} (CoGenT-A $\rightarrow$ CoGenT-B) remains an interesting problem to solve.
\end{itemize}

@@

\headerbox{MAC drawbacks on CLEVR}{name=mac-failures, column=1, below=experiments}{
	\vspace{-10pt}
	\begin{figure}[H]
		\includegraphics[width=0.60\textwidth]{../img/fail_mac_cogent_b_shape.png}
		\caption{There is a large gray thing that is on the right side of the big gray cylinder left of the large ball that is on the right side if the cyan rubber sphere; what is its shape?}
		\label{fig:mac_failure}
	\end{figure}
	\vspace{-20pt}
	\begin{itemize}
		\compresslist
		\item[$\bullet$] Asked about the shape of the leftmost gray cylinder, the model correctly finds it, (cf. \emph{visual attention map}), and refers to it using its color (\emph{attention over the question words}).
		\item[$\bullet$] Yet, predicts the shape as \textbf{cube}, as it never saw \emph{gray cylinders} during training, but saw \emph{gray cubes}.
		\item[$\rightarrow$] Indicate that MAC does not separate shape from color, but has a better understanding of colors (as found the object by its color).
	\end{itemize}
}

\headerbox{References}{name=references, column=1, below=mac-failures}{
	\small
	\vspace{-8pt}
	\renewcommand{\refname}{}
	\bibliographystyle{alpha}
	\bibliography{../vigil_bibliography}
}

\end{poster}
\end{document}
